# A transfer learning algorithms for different data domains

Combining quantitative (spatial) proteomics and (binary) annotation
features - [slides](https://github.com/ComputationalProteomicsUnit/Intro-Integ-Omics-Prot/blob/master/thetatut.pdf?raw=true).

### Example code

#### Loading the software and data

```{r env, eval=FALSE}
library("pRoloc")
library("pRolocdata")
data(andy2011)
```

#### Preparing the auxiliary data
```{r aux, eval=FALSE}
ap <- setAnnotationParams(inputs =
                              c("Homo sapiens",
                                "UniProt/Swissprot ID"))

andygoset <- makeGoSet(andy2011)
```

#### Optimising weights
```{r thetaopt, eval=FALSE}
thopt <- thetaOptimisation(andy2011, andygoset)
plot(thopt)
```

#### Predicting sub-cellular localisation
```{r thetaclass, eval=FALSE}
th <- getParams(thopt)
thes <- thetaClassification(andy2011, andygoset, bestTheta = th)
```

### References

Gatto L, Breckels LM, Burger T, Nightingale DJ, Groen AJ, Campbell C,
Nikolovski N, Mulvey CM, Christoforou A, Ferro M, Lilley KS. A
foundation for reliable spatial proteomics data analysis. Mol Cell
Proteomics. 2014 Aug;13(8):1937-52. doi: 10.1074/mcp.M113.036350. Epub
2014 May 20. PubMed
PMID:[24846987](http://www.ncbi.nlm.nih.gov/pubmed/24846987); PubMed
Central PMCID:PMC4125728.

Gatto L, Breckels LM, Wieczorek S, Burger T, Lilley KS.
Mass-spectrometry-based spatial proteomics data analysis using pRoloc
and pRolocdata. Bioinformatics. 2014 May 1;30(9):1322-4. doi:
10.1093/bioinformatics/btu013. Epub 2014 Jan 11. PubMed
PMID:[24413670](http://www.ncbi.nlm.nih.gov/pubmed/24413670); PubMed
Central PMCID:PMC3998135.

Wu P, Dietterich WG.
[Improving SVM accuracy by training on auxiliary data sources](http://citeseer.ist.psu.edu/viewdoc/summary?doi=10.1.1.94.594).
ICML 2004.

Breckels LM, Holden S, Christoforou A, Lilley KS, Gatto L. A Transfer
Learning Framework for Spatial Proteomics Data. In prep.


| [Home](./README.md) | [Caveats](./caveats.md) | [Mapping](./mapping.md) | [Transfer learning](./transfer-learning.md) |
